\small
\vspace{8pt}
\subsection*{Grattan Institute Technical Report, March 2016}

\raggedright

This technical report was written by Dr Peter Goss, Grattan Institute School Education Program Director, and Dr Cameron Chisholm, Grattan Institute Senior Associate. It was prepared to accompany the Grattan Institute Report, \textit{Widening gaps: What NAPLAN tells us about student progress}. The purpose is to present the data and methodology used in the analysis, with a discussion exploring robustness and sensitivity.

We would like to thank the members of Grattan Institute's School Education Reference Group for their helpful comments on the methodology, as well as numerous industry participants and officials for their input. We would also like to thank two experts who specifically reviewed this technical report.

The opinions in the technical report are those of the authors and do not necessarily represent the views of Grattan Institute’s founding members, affiliates, individual board members reference group members or reviewers. Any remaining errors or omissions are the responsibility of the authors.

Grattan Institute is an independent think-tank focused on Australian public policy. Our work is independent, practical and rigorous. We aim to improve policy outcomes by engaging with both decision-makers and the community.

For further information on the Institute's programs, or to join our mailing list, please go to:
\url{http://www.grattan.edu.au/}

\footnotesize

The technical report may be cited as:
\newline
Goss, P., and Chisholm, C., 2016, \textit{Widening gaps: what NAPLAN tells us about student progress. Technical Report}, Grattan Institute

All material published or otherwise created by Grattan Institute is licensed under a Creative Commons Attribution-NonCommercial-ShareAlike 3.0 Unported License
\normalsize